Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-10 krs-survey.tex
Filled section on task planning

\subsubsection{Planning}
\label{sect|planning}

@@

>>>>

\subsubsection{Task Planning}
\label{sect|planning}

@@

Symbolic task planning is the ability for a robot to select a sequence of
actions in order to reach a given final state. This capability is closely
related to the previously mentioned projection and legality tasks: for a robot
to plan, it must be able to build hypothetical states of the world that would
follow from the successive application of actions (prediction task), and at
each step, select possible, legal actions based on their pre-conditions
(legality task). As already mentioned, these tasks are highly non-monotonic.

Symbolic task planning in general is a large research
field\cite{Russell2009planning}. The so-called Classical Planning Problem,
first, is characterised by a unique known initial state, durationless
deterministic actions which can be taken only one at a time, and a single
agent. STRIPS and PDDL are amongst the commonly used languages for representing
such planning problems.

Planning with nondeterministic durationless actions with probabilities can be
represented as discrete-time \emph{Markov decision processes} (MDP), and when
full observability is replaced by partial observability, we deal with
\emph{partially observable Markov decision process} (POMDP).

\emph{Hierarchical Task Networks} (HTN) are another common formalism for
planning problems, where an initial set of tasks (\emph{High Level Tasks}, HLA)
is decomposed into either primitive actions or a new set of subtasks.

From the observation that the core reasoning techniques (back and forward
chaining) are shared between planners and reasoners used in knowledge
representation systems, task planning can be considered within the KRS.

It is however common to rely on external components dedicated to symbolic task
planning (in particular because of the non-monotonicity requirements) with a
tight link to the KRS for domain retreival and/or resulting plan storage.

%An extensive report on task modeling in OWL ontologies in appendix
